%\begin{alwayssingle} 
%    \thispagestyle{empty}
%    \begin{center}
%        \vspace*{1.5cm}
%        {\Large \bfseries Acknowledgements}
%    \end{center}
%
%    \vspace{0.5cm}
%    \begin{quote}
%
%    I guess something goes here...
%
%    \end{quote}
%\end{alwayssingle}

%%Alternative 

\begin{alwayssingle} 
    \thispagestyle{empty}
    \begin{center}
        \vspace*{1.5cm}
        {\Large \bfseries Acknowledgements}
    \end{center}
    \vspace{0.5cm}
    I owe a great deal of gratitude to a number of people, without whom this thesis would not have been possible.
    First and foremost, I would like to thank my supervisor, Malcolm John, for his invaluable guidance and encouragement throughout my DPhil.  

    During the last three and a half years I've crossed paths with different people, all of whom have made my time here a really enjoyable experience. 

    I'm grateful to everyone in the Oxford \lhcb group for their help and support, and for cultivating a friendly, enthusiastic environment. I'm look forward to spending the next two years here as a postdoc.
    I'd like to thank my friends in the wider Oxford Particle Physics group for making our lunches, coffee breaks and pub trips a welcome distraction from work. 

    I'd also like to thank the people I've met as a member of St Peter's College; in particular the friendly, welcoming MCR community. Whilst at St Peter's I joined the St Peter's College Boat Club where I tried rowing for the first time. It's safe to say I enjoyed it and I'm grateful to my fellow crews for making even the coldest of winter outings a rewarding experience.     
    
    One of the highlights of my DPhil was definitely the 18 months I spent based at CERN. I had the opportunity to work and live with some brilliant people; too many to name. I was lucky enough to spend a large amount of time in the winter skiing and summer cycling. All this wouldn't have been possible without a great group of friends. 

    Finally, I would like to thank my parents and sister for their endless love and support.   


\end{alwayssingle}
